Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-14 docs/ms.tex
Update ms.tex

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as e = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
of Universe ,we expect $\phi$has a uniform distribution from 0 to
$\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

So $<\epsilon_{\ell}>$ can be adopted as an estimator of g.

However in our hierachical Bayesian approach we are able to obtain
the posterior distribution of g ,starting from the same formulas.

Suppose we know the ellipticity distribution of unlensed galaxies
based on some parasmeters $\alpha$,the likelihood of reduced shear
$g$ and parameter $\alpha$ is like:

@@

$\ell_{i}(\alpha|data_{i})$ is the marginalized likelihood function
calculated with data in the ith patch.From this formula we can see
how better estimation of $\alpha$ will be obtained if we infer more
sky patches simultaneously.

>>>>

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
of Universe ,we expect $\phi$ has a uniform distribution from 0 to
$\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

Therefore $<\epsilon_{\ell}>$ can be adopted as an estimator of g.

However in our hierachical Bayesian approach we are able to obtain
the posterior distribution of g ,based on the assumption  $\phi$ has a uniform distribution and galaxies in different
sky patches have the same intrinsic shape distribution.

Suppose we know the ellipticity distribution of unlensed galaxies
based on some parasmeters $\alpha$,then we can write the likelihood of reduced shear and $\alpha$:

@@

$\ell_{i}(\alpha|data_{i})$ is the marginalized likelihood function
calculated with data in the ith patch.From this formula we can see
how better estimation of $\alpha$ will be obtained if we infer more
sky patches simultaneously. With better knowledge on $\alpha$ we can in turn have better estimates on reduced shear g.
